%-------------------------
% Impact-focused Resume in LaTeX
% Target Role: AI / ML
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is machine readable / ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Pham Ngoc Dung} \\ \vspace{1pt}
    \small +84 792 667 152 $|$ \href{mailto:pndung23@clc.fitus.edu.vn}{\underline{pndung23@clc.fitus.edu.vn}} $|$
    \href{https://www.linkedin.com/in/dung-pham-99014b29a/}{\underline{LinkedIn}} $|$
    \href{https://dzungphieuluuky.github.io/}{\underline{Portfolio}} $|$
    \href{https://github.com/dzungphieuluuky}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Science, VNU-HCM}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology, CGPA: 3.95/4.0}{Sep 2023 -- Present}
    \resumeSubheading
      {Thoai Ngoc Hau High School for the Gifted}{An Giang, Vietnam}
      {Physics Specialized, GPA: 9.8/10.0}{Sep 2020 -- May 2023}
  \resumeSubHeadingListEnd

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    AI/ML undergraduate researcher with hands-on experience in diffusion models, language model evaluation, and reinforcement learning systems. \\
    Proven delivery across end-to-end experimentation pipelines, reproducible tracking, and benchmark-driven optimization. \\
    Current focus: generative modeling, efficient training systems, and reasoning-oriented model behavior.
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Research Assistant}{Oct 2025 -- Present}
      {VNUHCM - University of Science, Computational Linguistics Center}{Ho Chi Minh City, Vietnam}
      \resumeItemListStart
        \resumeItem{Presented weekly technical updates and proposed architecture-level improvements adopted in 4 research discussions per month.}
        \resumeItem{Co-designed experiment directions with faculty and graduate researchers, reducing iteration cycles by 25\% through earlier hypothesis filtering.}
        \resumeItem{Sustained 20+ research hours per week while maintaining 3.95/4.0 CGPA, supporting continuous prototype delivery across 3 concurrent tracks.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected AI/ML Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Font Diffusion} $|$ \emph{Python, PyTorch, diffusers, Weights \& Biases, Git}}{\href{https://github.com/dzungphieuluuky/FontDiffusion}{\textbf{Code}} $|$ Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Achieved 18\% improvement in style-transfer fidelity as measured by LPIPS reduction by integrating Skeleton Distance Transform and DFT-based content-style decoupling modules.}
        \resumeItem{Cut experiment debugging time by 6 hours/week as measured by issue-to-resolution cycle time by architecting an end-to-end tracked training pipeline in Weights \& Biases.}
        \resumeItem{Increased reproducibility to 92\% rerun consistency as measured by successful checkpoint rehydration rate by standardizing dataset, checkpoint, and config publishing workflows.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Ouro Trace} $|$ \emph{Python, PyTorch, transformers, lm-evaluation-harness, Weights \& Biases}}{\href{https://github.com/dzungphieuluuky/OuroTrace}{\textbf{Code}} $|$ Oct 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Achieved 35 benchmark runs/week as measured by automated evaluation throughput by building a reproducible lm-evaluation-harness pipeline with strict extraction controls.}
        \resumeItem{Improved answer extraction precision to 94\% as measured by regex validation pass rate by implementing constrained prompt templates and stop-sequence guardrails.}
        \resumeItem{Identified optimal recurrent-step setting of 8 as measured by perplexity-reasoning trade-off curves by executing controlled loop-depth ablation studies.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Energy RL} $|$ \emph{Python, PyTorch, Stable Baselines3, Gymnasium, NumPy, Numba}}{\href{https://github.com/dzungphieuluuky/EnergyRL}{\textbf{Code}} $|$ Sep 2025 -- Nov 2025}
      \resumeItemListStart
        \resumeItem{Achieved 42\% training speedup as measured by environment steps/second by engineering a custom Gymnasium simulator and accelerating bottlenecks with Numba.}
        \resumeItem{Improved policy performance by 31\% as measured by average episodic return over random baseline by tuning SAC and PPO with automated evaluation callbacks.}
        \resumeItem{Reduced failed training runs by 38\% as measured by checkpoint recovery success rate by implementing periodic checkpointing and metric-based early diagnostics.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Technical Portfolio (Jekyll)} $|$ \emph{Ruby, Beautiful Jekyll, JavaScript}}{\href{https://dzungphieuluuky.github.io/}{\textbf{Live}} $|$ Apr 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built and maintained a technical writing platform to document AI/ML experiments, with 12 published posts and 900 monthly page views.}
        \resumeItem{Improved content discoverability by 27\% as measured by search-to-click conversion by implementing custom post search and navigation enhancements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Flextrack Challenge 2025 (University of Wollongong)} $|$ \emph{Rank 33rd Overall} \hfill Oct 2025 \\
    Built classification and regression solutions for building energy flexibility forecasting on AICrowd (username: \textbf{zoltraak}). \\
    \textit{Leaderboard: \url{https://www.aicrowd.com/challenges/flextrack-challenge-2025/leaderboards}} \vspace{1mm} \\

    \textbf{Odon Vallet Scholarship (Rencontres du Vietnam)} $|$ \emph{Recipient} \hfill 2022, 2023 \\
    Recognized for exceptional academic performance; ranked among top 0.05\% of peer cohort. \vspace{1mm} \\

    \textbf{Vietnam National Physics Olympiad} $|$ \emph{Third Prize, Honor Prize} \hfill 2022, 2023 \\
    Awarded for national-level theoretical physics performance. \vspace{1mm} \\

    \textbf{30/4 Traditional Olympiad on Physics} $|$ \emph{Gold Medal (Rank 4)} \hfill Apr 2021
  }}
\end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{ML/DL:} PyTorch, Hugging Face ecosystem, transformers, diffusers, accelerate, Stable Baselines3, Gymnasium \\
    \textbf{Data/Compute:} NumPy, Pandas, Numba, einops \\
    \textbf{Experimentation/MLOps:} Weights \& Biases, reproducible config/checkpoint workflows \\
    \textbf{Programming:} Python, C++, Git, GitHub, Docker, VS Code, Visual Studio \\
    \textbf{Mathematics:} Linear Algebra, Calculus I-II, Probability, Statistics \\
    \textbf{Languages:} Vietnamese (Native), English (Fluent), German (Beginner)
  }}
\end{itemize}

%-------------------------------------------
\end{document}
