%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Pham Ngoc Dung} \\ \vspace{1pt}
    \small 0792667152 $|$ \href{mailto:pndung23@clc.fitus.edu.vn}{\underline{Education Contact}} $|$ 
    \href{https://www.linkedin.com/in/dung-pham-99014b29a/}{\underline{LinkedIn}} $|$
    \href{https://dzungphieuluuky.github.io/synaptheos/}{\underline{Portfolio}} $|$
    \href{https://github.com/dzungphieuluuky}{\underline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Science, VNU-HCM}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology, CGPA: 3.95/4.0}{Sep. 2023 -- Present}
    \resumeSubheading
      {Thoai Ngoc Hau High School for the Gifted}{An Giang}
      {Physics Specialized, GPA: 9.8/10.0}{Sep. 2020 -- May 2023}
  \resumeSubHeadingListEnd

%-----------RESEARCH INTEREST-----------
\section{Research Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Generative Modeling:} Diffusion models, diffusion-based approach for few-shot generation and style-content disentanglement. \\
     \textbf{Large Language Models:} Looped language models, diffusion-based large language models (LLaDA). \\
     \textbf{Reinforcement Learning:} Sample efficiency, exploration-exploitation trade-offs, diffusion-based approach for policy learning and trajectory optimizations in model-based reinforcement learning.
    }}
 \end{itemize}
 
 %-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{Oct 2025 -- Present}
      {VNUHCM - University of Science, Computational Linguistics Center}{Ho Chi Minh City, Vietnam}
      \resumeItemListStart
        \resumeItem{Present technical research progress and proposed methodological advancements during weekly seminars with the Principal Professor.}
        \resumeItem{Collaborate with faculty and graduate researchers to brainstorm and refine architectural optimizations.}
        \resumeItem{Maintain a dedicated research commitment of 20+ hours per week, balancing high-level assistantship responsibilities with a 3.95/4.0 CGPA curriculum.}      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
    %   {Information Technology Support Specialist}{Sep. 2018 -- Present}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Communicate with managers to set up campus computers used on campus}
    %     \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
    %     \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
    % \resumeItemListEnd

    % \resumeSubheading
    %   {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
    %     \resumeItem{Developed a game in Java to test the generated dungeons}
    %     \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
    %     \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
    %     \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
    %     \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Dedicated Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Font Diffusion} $|$ \emph{Python, Git, PyTorch, diffusers, Wandb}}{\href{https://github.com/dzungphieuluuky/FontDiffusion}{\textbf{Code}} $|$ Oct 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Engineered an end-to-end machine learning pipeline for high-fidelity dataset generation and model training, utilizing Weights and Biases for granular experiment tracking and reproducibility.}
            \resumeItem{Integrated FSTDiff innovations and developed custom modules using Skeleton Distance Transformation and Discrete Fourier Transform (DFT) to effectively decouple content features from style features.}
            \resumeItem{Designed and implemented a novel loss function (identity mapping) to bolster content-invariance, which significantly streamlined the style transformation learning process.}
            \resumeItem{Streamlined research collaboration and version control by publishing curated datasets and model checkpoints to the Hugging Face ecosystem.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Ouro Trace} $|$ \emph{Python, Git, PyTorch, transformers, Wandb, lm-evaluation-harness}}{\href{https://github.com/dzungphieuluuky/OuroTrace}{\textbf{Code}} $|$ Oct 2025 -- Dec 2025}
          \resumeItemListStart
            \resumeItem{Benchmarked the performance and behavioral dynamics of Ouro Looped Language Models based on recent ByteDance research using reasoning tasks, \textbf{lm-evaluation-harness} and experimental tracking with \textbf{Wandb}.}
            \resumeItem{Engineered dedicated generation controls by implementing custom system prompts, strict stop sequences, and parameter tuning to ensure consistent and accurate answer extraction via regular expression parsing.}
            \resumeItem{Conducted comparative analysis between looped architectures and traditional language models , evaluating them via perplexity benchmarks and reasoning-intensive datasets.}
            \resumeItem{Discovered critical insights into the relationship between recurrent steps and reasoning performance, identifying the optimal recurrent steps value to maximize model performance on reasoning tasks while using resources efficiently.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Energy RL} $|$ \emph{Python, Git, PyTorch, Stable Baselines 3, Gymnasium, NumPy, Numba}}{\href{https://github.com/dzungphieuluuky/EnergyRL}{\textbf{Code}} $|$ Sep 2025 -- Nov 2025}
          \resumeItemListStart
            \resumeItem{Developed a Reinforcement Learning agent to optimize network resource management under non-stationary energy demands.}
            \resumeItem{Architected a custom environment simulator using Gymnasium and NumPy, later implementing Numba to accelerate processing speeds for high-performance experience collection.}
            \resumeItem{Evaluated the efficacy of PPO and SAC algorithms by implementing custom callbacks for real-time metric logging, automated evaluation, and checkpointing.}
            \resumeItem{Achieved a performance score of 60/100, demonstrating significant improvements against random baselines even when operating under significant computational and hardware constraints.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Personal Portfolio} $|$ \emph{Ruby, Beautiful Jekyll}}{\href{https://dzungphieuluuky.github.io/synaptheos/}{\textbf{Link}} $|$ Apr 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Architected and maintained a professional technical portfolio using Ruby and the Beautiful Jekyll framework  to showcase personal achievements.}
            \resumeItem{Authored several technical blog posts for documenting learning journeys and sharing personal experience when working with deep learning projects.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% -----------Awards----------------------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Flextrack Challenge 2025 (University of Wollongong)} $|$ \emph{Rank 33rd Overall} \hfill Oct 2025 \\
     Developed a classification model (track 1) and regression model (track 2) for Detecting Energy Flexibility in Buildings; hosted on AICrowd (Username: \textbf{zoltraak}). \\
     \textit{Leaderboard: \url{https://www.aicrowd.com/challenges/flextrack-challenge-2025/leaderboards}} \vspace{1mm} \\
     
     \textbf{Odon Vallet Scholarship (Rencontres du Vietnam)} $|$ \emph{Recipient} \hfill 2022, 2023 \\
     Awarded for exceptional academic performance; recognized as top 0.05\% among students of the same grade in the school. \vspace{1mm} \\
     
     \textbf{Vietnam National Physics Olympiad} $|$ \emph{Third Prize \& Honor Prize} \hfill 2022, 2023 \\
     Nationwide competition for theoretical physics knowledge and understanding. \vspace{1mm} \\
     
     \textbf{30/4 Traditional Olympiad on Physics} $|$ \emph{Gold Medal (Rank 4th)} \hfill Apr 2021 \\
     Achieved 4th place among elite students of the same grade in Physics from Southern Vietnam.
    }}
 \end{itemize}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Deep Learning}{: PyTorch, Hugging Face ecosystem, transformers, diffusers, accelerate, Stable Baselines 3, Farama Foundation Gymnasium } \\
     \textbf{Data Science \& Numerical Computing}{: NumPy, Pandas, Numba, Einops } \\
     \textbf{MLOps}{: Weights and Biases (Wandb) } \\
     \textbf{Programming}{: Python, C++, Git, GitHub, Docker, VS Code, Visual Studio} \\
     \textbf{Mathematics Background}{: Linear Algebra, Calculus I \& II, Probability \& Statistics} \\
     \textbf{Languages}{: Vietnamese (Native), English (Fluent), German (Beginner) }
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
